Propositions as Sessions, Mechanically

### 2015-04-20 paper/presentation.tex
Added some more details for presentation script.

the formalisation i present here is based on recent work providing a logical
foundation for understanding session types. in particular i present work
towards a formalisation of Wadler's original CP/GV system which describes a
two-tier type system with session types. A high-level overview of the system
is as follows: we have a process calculus CP with operators from classical
linear logic, a high-level functional language GV with session types, and a
translation from GV to CP which interprets operators in classical linear logic
as session types.

@@

by classical linear logic i mean a logic where negation is an involution which
restricts the use of certain rules on resources, namely that all linear
resources must be used (corresponding to prohibiting weakening) and that one
cannot duplicate a linear resource (corresponding to contraction). some
operators in the CP calculus are presented. the interpretation of tensor
product is output of A and continue as B. The dual of this is input of A and
continue as the negation of B. Thus negation in classical linear logic
corresponds to session duality.

@@

the formalisation i will describe today regards this
connection, I will present work towards a formalisation of the system GV/CP
originally described by Phil Wadler was the aim of this project to mechanise
it. it provides a basis for further additions and also provides some
properties that may be desirable such as deadlock freedom. the formalisation
provides a means to gain more confidence in the proofs but also assists in
extending them to account for the effects of additions.

\begin{comment}
whats the problem
what have others done
why are we doing it
what did we do
what have we learned
\end{comment}
\begin{frame}
\frametitle{Preamble}
\item Propositions as Sessions
\item system features
\item Coq
\item encoding
\item subject reduction theorem
\item difficulties in formalisation
\item implications
\item future work
\end{frame}

>>>>

the formalisation i present here is an encoding of a system in the Coq proof
assistant. it is based on a two-tier system providing a logical foundation for
understanding session types. A high-level overview of the system is as
follows: we have a process calculus CP with operators from classical linear
logic, a high-level functional language GV with session types, and a
translation from GV to CP which interprets operators in classical linear logic
as session types.

@@

by classical linear logic i mean a logic where negation is an involution which
restricts the use of certain rules on resources, namely that all linear
resources must be used (corresponding to prohibiting weakening) and that one
cannot duplicate a linear resource (corresponding to contraction). some
operators in the CP calculus are presented as they appear in the Coq encoding
(note that they are very similar to their informal counterparts). the
interpretation of tensor product is output of A and continue as B. The dual of
this is input of A and continue as the negation of B. Thus negation in
classical linear logic corresponds to session duality.

@@

subject reduction is formalised using a relation on processes

cut elimination is not currently proven since we require a termination measure
on the length of a derivation and a relationship between the subprocesses of a
cut. other work based on formalising logics where the derivations are explicit
may be inspirational

the translation seems to require a duplication of the specifications for cp
and gv typing rules not done

what can we show them for the failures?

here are some issues and things learnt! -- our guidelines are all about
modularisation, representation, library reuse, automation!

\begin{frame}
\frametitle{Preamble}
\item Propositions as Sessions
\item system features
\item Coq
\item encoding
\item subject reduction theorem
\item difficulties in formalisation
\item implications
\item future work
\end{frame}
